\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Mohammed Niaz Ul Haque}}\\
	Scarborough, ON $\cdot$ theniaz619@gmail.com $\cdot$ (647) 657-6450\\
	linkedin.com/in/mohammed-niaz-ul $\cdot$ github.com/Niaz-Ul-Haque\\
\end{center}
%==== Summary ====%
\vspace*{10mm}

\vspace*{2mm}

Mohammed Niaz Ul Haque\\
121 Donside Drive\\
Scarborough, ON M1L 1P9\\
(647) 657-6450\\
theniaz619@gmail.com\linebreak\\\\

\\June 18, 2021\linebreak\\

Kevin Yoo\\
Ontario Treasury Board Secretariat\\
222 Jarvis Street\\
Toronto, ON M7A 0B6\linebreak\\
\linebreak
Dear Mr. Yoo:\linebreak\\

\linebreak
This letter is to express my interest in your posting on the Seneca Coop Job Postings for a Junior Web Developer. With an almost completed Advanced Diploma in Computer Programming and Analysis, and hands-on experience using front-end technologies like AngularJS, ReactJS, and Node to create and implement web applications, I am confident I will be an asset to your organization.\linebreak
\linebreak
I enjoy being challenged and engaging with projects that require me to work outside my comfort and knowledge set, as continuing to learn new languages and development techniques are important to me and the success of your organization.\linebreak\\\linebreak
\linebreak
Your listed requirements closely match my background and skills. A few I would like to highlight that would enable me to contribute to your bottom line are:\linebreak\\\linebreak
\linebreak
$\cdot$ Highly skilled in designing, testing, and developing web applications\\
$\cdot$ Knowledgeable of both front-end \& back-end development best practices\\
$\cdot$ Thorough understanding of routing and database concepts\\
$\cdot$ Continuous improvements on my knowledge base in the field of web design and development.\\
$\cdot$ Experience contributing to open source software projects and web based side projects.\\
$\cdot$ Hands-on web troubleshooting experiences\linebreak\\

I’ve attached a copy of my resume that details my projects and experience in software development. I can be reached anytime via my cell phone, 647-657-6450 or via email at theniaz619@gmail.com.\linebreak\\\linebreak
\linebreak
Thank you for your time and consideration. I look forward to speaking with you about this opportunity.\linebreak\\\linebreak\linebreak
\linebreak
Sincerely,\linebreak

Mohammed Niaz Ul Haque\linebreak

%==== Experience

\ 
\end{document}
